### 2016-07-25 finalText/theorBack.tex
Final Version of the Text and Short Paper

\subsubsection{Training -- SPSA}\label{sec:training_lstm}
Since this work aims to perform on-chip learning, it is important to find a suitable learning scheme. Since I am aiming at an hardware implementation, and although the memory resources of current FPGAs are abundant, one must find an algorithm that uses the less memory as possible (at the smallest performance cost possible), in order to use the additional memory, for instance, to add additional LSTM cells that can improve the performance of our system. 
That being said, we see that the usual training algorithms for LSTM cells -- i.e. Real-Time Recurrent Learning (RTRL), Truncated Backpropagation Through Time (BPTT) or a mixture of both~\cite{Graves05}~\cite{Hoch97}~\cite{Greff15} -- usually involve the storage of the deltas of each layer for every time instant in the training epoch (from $0$ to $T$), which is a highly non-scalable solution both in terms of memory and performance. A most efficient approach to training times series dependant structures like LSTM is the use of \textbf{Simultaneous Perturbation Stochastic Approximation} (SPSA)~\cite{Spall98}.  The main idea of this technique is, instead of explicitly evaluating the gradients for the cost function at each time step, to perform a random walk in the neighbourhood of the current weight matrix, in the weight space, and approximate the new weight update by the approximation of the gradient of the cost function that resulted from that random walk. The weight update for the $i$-th weight at the time step $t$ is given by

@@

\begin{equation}\label{eq:taylor}
    \Delta w_i^{(t)} = s_i^{(t)} (\mb{s}^{(t)})^T \frac{\partial J(\mb{w}^{(t)})}{\partial \mb{w}} +
                        \frac{c s_i^{(t)}}{2} (\mb{s}^{(t)})^T \frac{\partial^2 J(\mb{w}^{(t)})}{\partial \mb{w}^2}  (\mb{s}^{(t)}) 
\end{equation}
If the random sign vector $\mb{s}^{(t)}$ is chosen carefully so that the expected value of the vector at the $i$-th position is zero, $E(s_i^{(t)})$, and the signs of two different components $i$ and $j$, at different time-steps, are independent (i.e. $E(s_i^{(t_1)}s_j^{(t_2)}) = \delta_{ij}\delta_{t_1 t_2}$, where $\delta$ is the Kronecker fuction), taking the \emph{Expected Value} of equation~\ref{eq:taylor} yields

>>>>

\subsubsection{Training -- SPSA}\label{sec:training_lstm}
Since this work aims to propose an on-chip learning circuit, it is important to find a suitable learning scheme. Since I am aiming at an hardware 
implementation, and although the memory resources of current FPGAs are abundant, one must find an algorithm that uses as less memory as possible 
(at the smallest performance cost possible). That being said, we see that the usual training algorithms for LSTM cells --- i.e. Real-Time Recurrent 
Learning (RTRL), Truncated Backpropagation Through Time (BPTT) or a mixture of both~\cite{Graves05}~\cite{Hoch97}~\cite{Greff15} --- usually involve 
the storage of the deltas of each layer for every time instant in the training epoch (from $0$ to $T$), which is a highly non-scalable solution both 
in terms of memory and performance. A most efficient approach to training times series dependant structures like LSTM is the use 
of \textbf{Simultaneous Perturbation Stochastic Approximation} (SPSA)~\cite{Spall98}.  The main idea of this technique is, instead of explicitly evaluating 
the gradients for the cost function at each time step, to perform a random walk in the neighbourhood of the current weight matrix, in the weight space, and 
approximate the new weight update by the approximation of the gradient of the cost function that resulted from that random walk. The weight update for the $i$-th 
weight at the time step $t$ is given by

@@

\begin{equation}\label{eq:taylor}
    \Delta w_i^{(t)} = s_i^{(t)} (\mb{s}^{(t)})^T \frac{\partial J(\mb{w}^{(t)})}{\partial \mb{w}} +
                        \frac{c s_i^{(t)}}{2} (\mb{s}^{(t)})^T \frac{\partial^2 J(\mb{w}^{(t)})}{\partial \mb{w}^2}  (\mb{s}^{(t)}) 
\end{equation}
If the random sign vector $\mb{s}^{(t)}$ is chosen carefully so that the expected value of the vector at the $i$-th position is zero, $E(s_i^{(t)})$, and the signs of two different components $i$ and $j$, at different time-steps, are independent (i.e. $E(s_i^{(t_1)}s_j^{(t_2)}) = \delta_{ij}\delta_{t_1 t_2}$, where $\delta$ is the Kronecker function), taking the \emph{Expected Value} of equation~\ref{eq:taylor} yields
